Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
Copy-edit list of tasks

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Google search for the population of Zimbabwe. 
\item On Youtube, find a video playing Bach's ``Ode to Joy.'' 
\item Find the Amazon best-sellers in ``Movies \& TV.''
\item On Yahoo, find the exchange rate of dollars to euros.
\item Find the Wikipedia ``History'' portal's featured article. 
\item On Twitter, find the currently trending topics.
\item On Bing Maps, find directions from Time Square to Carnegie Hall.
\end{itemize}

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Google search for the population of Zimbabwe. 
\item On YouTube, find a video playing Bach's ``Ode to Joy.''
\item Find the Amazon best-sellers in ``Movies \& TV.''
\item On Yahoo, find the exchange rate of Dollars to Euros.
\item Find the Wikipedia ``History'' portal's featured article. 
\item On Twitter, find the currently trending topics.
\item On Bing Maps, find directions from Times Square to Carnegie Hall.
\end{itemize}
